Methodology for Assessing the State of the Practice for Domain X

### 2020-12-01 StateOfPractice/Methodology/Methodology.tex
Updates to methodology

@@

\begin{document}
\maketitle

@@

@@

The scope of this document is to conduct a current state of practice analysis of
software in a scientific computing domain for the purpose of understanding
quality and assisting in future development. We observe product, artifact, and
process quality in our analysis. We leave the assessment of scientific computing
software using performance benchmarks to other projects, such as the work of
\cite{kaagstrom1998gemm}. The methodology presented here is part of an overall
assessment of the impact of model driven engineering and code generation on the
sustainability of scientific computing software. The research proposal for this
assessment, which contains a more detailed description of this state of practice
exercise, can be found
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}{here}. The
research questions that this exercise will answer are found in Section
\ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to be taken.

>>>>

\ccsdesc{Software and its engineering}
\ccsdesc{Software and its engineering~Software product lines}
\ccsdesc{General and reference~Empirical studies}

\keywords{software quality, domain analysis, scientific computing software,
  research software, empirical measures, analytic hierarchy process}

@@

\begin{document}

\maketitle

@@

~\newpage

@@

The scope of this document is to conduct a current state of practice analysis of
software in a scientific computing domain for the purpose of understanding
quality and assisting in future development. We observe product, artifact, and
process quality in our analysis. We leave the assessment of scientific computing
software using performance benchmarks to other projects, such as the work of
\cite{kaagstrom1998gemm}. The methodology presented here is part of an overall
assessment of the impact of model driven engineering and code generation on the
sustainability of scientific computing software. The research proposal for this
assessment, which contains a more detailed description of this state of practice
exercise, can be found
\href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}
{here}. The research questions that this exercise will answer are found in
Section \ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to
be taken.
